Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Added Figure 13 (Didn't see any pattern with error)

@@

@@

@@

trimesh_removed_gau_tsne + trimesh_removed_gau_umap + trimesh_removed_gau_pacmap +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + five_gau_proj_tsne_model2 + five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 3) &
  theme(legend.position='none')
```

>>>>

## Compute error

error_df_gau_abs <- augment(
  df_bin_centroids = df_bin_centroids_gau1,
  df_bin = df_bin_gau1,
  training_data = training_data_gau,
  newdata = NULL,
  type_NLDR = "tSNE",
  col_start = "x")

error_df_gau_abs <- error_df_gau_abs |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

error_df_gau_abs <- error_df_gau_abs |>
  bind_cols(tsne_gau_scaled |>
              select(-ID))

error_df_gau_tsne <- error_df_gau_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.3, 0.66)) + ylim(c(-0.01, 0.35)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("a3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

## Compute error

error_df_gau_abs <- augment(
  df_bin_centroids = df_bin_centroids_gau1,
  df_bin = df_bin_gau1,
  training_data = training_data_gau,
  newdata = NULL,
  type_NLDR = "UMAP",
  col_start = "x")

error_df_gau_abs <- error_df_gau_abs |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

error_df_gau_abs <- error_df_gau_abs |>
  bind_cols(umap_gau_scaled |>
              select(-ID))

error_df_gau_umap <- error_df_gau_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.47, 0.5475)) + ylim(c(0.0125, 0.09)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("b3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

## Compute error

error_df_gau_abs <- augment(
  df_bin_centroids = df_bin_centroids_gau1,
  df_bin = df_bin_gau1,
  training_data = training_data_gau,
  newdata = NULL,
  type_NLDR = "PaCMAP",
  col_start = "x")

error_df_gau_abs <- error_df_gau_abs |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

error_df_gau_abs <- error_df_gau_abs |>
  bind_cols(pacmap_gau_scaled |>
              select(-ID))

error_df_gau_pacmap <- error_df_gau_abs |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(-0.02, 0.18)) + ylim(c(0.12, 0.32)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("c3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

trimesh_removed_gau_tsne + trimesh_removed_gau_umap + trimesh_removed_gau_pacmap +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + error_df_gau_tsne + error_df_gau_umap + error_df_gau_pacmap +
  plot_layout(guides = "collect", nrow = 3) &
  theme(legend.position='none')
```
